Further drift-magnetohydrodynamic modeling of linear tearing mode dynamics in tokamak plasmas

### 2021-12-06 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
Started linear paper

\section*{Acknowledgements}
This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742,

@@

\bibitem{error1} J.T.~Scoville, and R.J.~La\,Haye, Nucl.\ Fusion {\bf 43}, 250 (2003).
\end{thebibliography}

>>>>

\section{Introduction}
Tearing modes are slowly growing instabilities of ideally-stable tokamak plasmas that reconnect magnetic field-lines
at various resonant surfaces within the plasma, in the process degrading the plasma confinement.\cite{wes}
If tearing modes gorw to sufficiently large amplitude then they can trigger major disruptions.\cite{wes1}  Tokamak
plasma are observed to be particularly disruption prone when tearing modes {\em lock}\/ (i.e., become stationary in the
laboratory frame) to externally generated, resonant magnetic perturbations.\cite{vries}

It is well known that single-fluid resistive magnetohydrodynamics (MHD) offers a very poor description of
tearing mode dynamics in tokamak plasmas. 
For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion fluid dynamics,
necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius lengthscale}, below which electron and ion dynamics are further decoupled, 
into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
of Fitzpatrick \& Waelbroeck\,\cite{fw} (which is based on the original four-field model of Hazeltine, et al.\cite{haz}),
to determine the two-fluid response of a linear tearing layer in a tokamak plasma to an externally generated, 
resonant magnetic perturbation. However, the treatment of Cole \& Fitzpatrick failed to take into account the
strong anomalous perpendicular transport of particles and energy present in tokamak plasmas. The
aim of this paper is to correct this deficiency.

\section{Four-Field Model}

\section*{Acknowledgements}
This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under  contracts DE-FG02-04ER54742 and DE-SC0021156.

@@

\bibitem{wes} J.A.~Wesson, Nucl.\ Fusion {\bf 18}, 87 (1978).

\bibitem{wes1} J.A.~Wesson, et al.\ Nucl.\ Fusion {\bf 29}, 641 (1989).

\bibitem{vries} P.C. de Vries, et al.\ Nucl.\ Fusion {\bf 51}, 053018 (2011).

\bibitem{ara} G.~Ara, B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (NY) {\bf 112}, 443 (1978).

\bibitem{drake} J.F.~Drake, and Y.C.~Lee, Phys.\ Fluids {\bf 20}, 1341 (1977).

\bibitem{wal} F.L.~Waelbroeck, Phys.\ Plasmas {\bf 10}, 4040 (2003).

\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).

\bibitem{fw} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys. Plasmas {\bf 12}, 022307 (2005).

\bibitem{haz} R.D.~Hazeltine, M.~Kotschenreuther, and P.G.~Morrison, Phys.\ Fluids {\bf 28}, 2466 (1985).

\end{thebibliography}
